Diagnosis Visualizations

### 2023-05-24 Diagnosis_Vis.Rmd
Ridgeline plots!

cap = "**Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project <br> "

set.seed(12345)
ggplot(
  data = Mothership_Current_Long,
  mapping = aes(
    x = Days_complete_1,
    y = Disorder_Type,
    group = Disorder_Type)
  )+
  geom_jitter(
    size = 0.6,
    alpha = .5,
    colour = highlight_col
    )+
  geom_boxplot(
    outlier.shape = NA,
    colour = outline_col,
    fill = highlight_col,
    alpha = 0.3) +
  scale_x_continuous(
   breaks = c(0, 15, 30, 45, 60),
    limits = c(0.00, 60)
  ) +
  labs(
    x = "Number of Days In Partial Hospitalization Program",
    y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = st,
    caption = cap
    ) +
  theme_minimal(
    base_size = 30,
    base_family = "Commissioner"
    ) +
  theme(
    axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4,
       colour = alpha(dark_col, 0.2),
    ),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 20),
      colour = dark_col,
      size = 70
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 20),
      halign = 0,
      size = 28
    ),
    plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10)
    ),
    axis.text = element_text(colour = dark_col),
    axis.title = element_text(colour = dark_col),
    legend.position = "none",
    plot.margin = margin(15, 15, 10, 10)
  )

@@

>>>>

cap = "**Source:** Methods to Improve Diagnostic Assessment and Services (MIDAS) project <br> "

set.seed(12345)
ggplot(
  data = Mothership_Current_Long,
  mapping = aes(
    x = Days_complete_1,
    y = Disorder_Type,
    group = Disorder_Type)
  )+
  geom_jitter(
    size = 0.6,
    alpha = .5,
    colour = highlight_col
    )+
  geom_boxplot(
    outlier.shape = NA,
    colour = outline_col,
    fill = highlight_col,
    alpha = 0.3) +
  scale_x_continuous(
   breaks = c(0, 15, 30, 45, 60),
    limits = c(0.00, 60)
  ) + 
  labs(
    x = "Number of Days In Partial Hospitalization Program",
    y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = st,
    caption = cap
    ) +
  theme_minimal(
    base_size = 10,
    base_family = "Commissioner"
    ) +
  theme(
    axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4,
       colour = alpha(dark_col, 0.2),
    ),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 10),
      colour = dark_col,
      size = 17
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 10),
      halign = 0,
      size = 8
    ),
    plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10)
    ),
    axis.text = element_text(colour = dark_col),
    axis.title = element_text(colour = dark_col),
    legend.position = "none",
    plot.margin = margin(15, 15, 10, 10)
  )

@@

# CUXOS by Diagnosis

### Code
```{r}
# install.packages("ggridges")
library(ggridges)
library(ggplot2)
library(forcats)
```

```{r}
bg_col <- "#F9FBF2"
dark_col <- "#333333"

title = "Baseline Anxiety for Patients By Disorder Type"
subtitle = "Upon entrence of the partial hospitalization program, scores of anxiety are reported from the _Clinically Useful Anxiety Outcome Scale_ (CUXOS). The CUXOS is a 20 item measure used to assess symptoms of anxiety; a cutoff score of 20 suggests a possitive screen for a probable anxiety disorder. Mean CUXOS scores are reported for each disorder type below (i.e., _the black line_)."
cap = "**Symptom severity:** 0-10 (non-anxiety), 11-20 (minimal anxiety), 21-30 (mild anxiety), 31-40 (moderate anxiety), 41+ (severe anxiety) <br> <br> **Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project"

p <- ggplot(Mothership_Current_Long, aes(
  x = BL_CUXOS,
  y = Disorder_Type,
  fill = Disorder_Type)) +
  # geom_density_ridges(alpha=0.6,
  #                     rel_min_height = 0.05, 
  #                     scale = 2)+
   stat_density_ridges(quantile_lines = TRUE, alpha = 0.6, quantiles = 2, rel_min_height = 0.05, scale = 1.5) +
   scale_x_continuous(
   breaks = c(0, 20, 40, 60, 80),
   limits = c(0, 80)) +
  #theme_ridges() + 
  labs(
    x = "Baseline Score on CUXOS",
    #y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = subtitle,
    caption = cap) +
   theme_minimal(
    base_size = 10,
    base_family = "Commissioner"
    ) + 
    theme(legend.position = "none",
          axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4), 
    axis.title.y= element_blank(),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),    
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 5),
      colour = dark_col,
      size = 15
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 6),
      halign = 0,
      size = 8
    ),
     plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10),
      size = 7))
```

### Plot

```{r}
p
```

# Depression by disorder type

### Code
```{r}
bg_col <- "#F9FBF2"
dark_col <- "#333333"

title = "Baseline Depression for Patients By Disorder Type"
subtitle = "Upon entrence of the partial hospitalization program, scores of anxiety are reported from the _Clinically Useful Depression Outcome Scale_ (CUDOS). The CUXOS is a 18 item measure used to assess different symptoms of depression; A cut off score of 20 suggests a positive screen for probable major depression. Mean CUDOS scores are reported for each disorder type below (i.e., _the black line_)."
cap = "**Symptom severity:** 0-10 (non-depression), 11-20 (minimal depression), 21-30 (mild anxiety), 31-45 (moderate depression), 41+ (severe depression) <br><br> **Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project"

q <- ggplot(Mothership_Current_Long, aes(
  x = BL_CUDOS,
  y = Disorder_Type,
  fill = Disorder_Type)) +
  # geom_density_ridges(alpha=0.6,
  #                     rel_min_height = 0.05, 
  #                     scale = 2)+
   stat_density_ridges(quantile_lines = TRUE, alpha = 0.6, quantiles = 2, rel_min_height = 0.05, scale = 1.5) +
   scale_x_continuous(
   breaks = c(0, 20, 40, 60),
   limits = c(0, 64)) +
  #theme_ridges() + 
  labs(
    x = "Baseline Score on CUXOS",
    #y = "DSM-5 Disorder Subtype",
    title = title,
    subtitle = subtitle,
    caption = cap) +
   theme_minimal(
    base_size = 10,
    base_family = "Commissioner"
    ) + 
    theme(legend.position = "none",
          axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.major.x = element_line(
       linewidth = 0.4), 
    axis.title.y= element_blank(),
    plot.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),    
    panel.background = element_rect(
      fill = bg_col,
      colour = bg_col
    ),
    plot.title = element_text(
      family = "Commissioner",
        #this is the font
      margin = margin(b = 5),
      colour = dark_col,
      size = 15
    ),
    plot.subtitle = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      family = "Commissioner",
      hjust = 0,
      margin = margin(b = 5),
      halign = 0,
      size = 8
    ),
     plot.caption = element_textbox_simple(
      lineheight = 0.55,
      colour = dark_col,
      margin = margin(t = 10),
      size = 8))
```

### plot
```{r}
q
```
